Gaudeamus Figures

### 2017-01-18 inst/examples/20161117-manuscript.Rmd
title length analyses for JM until 1911

# Analysis time window
dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1828)

@@

>>>>

# Analysis time window
#dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1828)
dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1911)

@@

```{r title_length_by_lang, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
top.language <- setdiff(names(top(dfo, "language", 11)), "NA")

df <- dfo %>% filter(language %in% top.language) %>%
              group_by(publication_decade, language) %>%
              summarize(mean_title_length = mean(title_wordcount),
	      		n = n())

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length,
                     fill = language, color = language)) +
       geom_point(aes(size = n)) +
       geom_line() +
       #scale_y_log10() +
       ggtitle("Mean title word count (top language)")

### 2017-01-18 inst/examples/Gaudeamus.Rmd

years <- c(1764,1809,1863,1917)
p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
#       geom_point() +
       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
       ggtitle(paste("Julkaisutoiminta Turussa ", miny, "-", maxy, sep = "")) + 
       ylab("Dokumenttia (n)") +
       scale_x_continuous(labels = years, breaks = years) +
       xlab("Julkaisuvuosi")

@@

years <- c(1764,1809,1863,1917)
p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
#       geom_point() +
       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
       ggtitle(paste("Julkaisutoiminta Suomessa ", miny, "-", maxy, sep = "")) +               
       ylab("Dokumenttia (n)") +
       scale_x_continuous(labels = years, breaks = years) +
       xlab("Julkaisuvuosi")

>>>>

years <- c(1640, 1764,1809,1863,1917)
p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
#       geom_point() +
       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
       ggtitle(paste("Julkaisutoiminta Turussa ", miny, "-", maxy, sep = "")) + 
       ylab("Dokumenttia (n)") +
       scale_x_continuous(labels = years, breaks = years) +
       xlab("Julkaisuvuosi")

@@

years <- c(1640, 1764,1809,1863,1917)
p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
#       geom_point() +
       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
       ggtitle(paste("Julkaisutoiminta Suomessa ", miny, "-", maxy, sep = "")) +               
       ylab("Dokumenttia (n)") +
       scale_x_continuous(labels = years, breaks = years) +
       xlab("Julkaisuvuosi")
